Annual Analysis of Delays in TTC Streetcars for the year 2023

### 2024-09-27 paper/paper.qmd
Reupload file because they were added to the root

## Overview of dataset
The following data was made available from OpenData Toronto (@opendatatoronto) for the year 2023. The data was extracted from the server and saved locally using in a raw data folder using the instructions provided by the documentation. We note that this was the only available dataset with frequent updates and data dating back to 2014. Some of the features part of this dataset are date, time, incident, min delay, bound and location.

@@

The website doesn't provided information on how the data was sourced but we can assume that the data is recorded by taking the difference in the reported arrival time via the TTC app and the actual time the streetcar arrives at various stops. The collected data represents common types like characters, numeric and datetime. Therefore, for the purposes of this study, the procedures used to collect the data and their types are appropriate for our use and we do not require any extra information to make any assumptions them.

>>>>

## Overview of dataset
The following data was made available from OpenData Toronto (@opendatatoronto) for the year 2023. The data was extracted from the server and saved locally in a raw data folder using the instructions provided by the documentation. We note that this was the only available dataset with frequent updates and data dating back to 2014. Some of the features part of this dataset are date, time, incident, min delay, bound and location.

@@

The website doesn't provided information on how the data was sourced but we can assume that the data is recorded by taking the difference in the reported arrival time via the TTC app and the actual time the streetcar arrives at various stops. The collected data represents common types like characters, numeric and datetime. Therefore, for the purposes of this study, the procedures used to collect the data and their types are appropriate for our use and we do not require any extra information to make any assumptions about them.
